---
title: "Weight of Fish"
author: "Hayden Wood"
date: "Spring 2024"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(MASS)
```

## Read in fisy data
```{r}
fishALL = read_csv('Fish.csv')
```


# Predicting Fish Weight


## Perch

```{r}
perchFish = filter(fishALL, Species=='Perch') 
perchModel = lm(Weight~Length1+Length2+Length3+Height+Width, data= perchFish)
summary.lm(perchModel)
```


### Best Models
We find best models for for all three species

```{r}
best_models_perch <- step(perchModel)
```

```{r}
summary.lm(best_models_perch)
```



### Best Two regressor model


```{r}
best_two_regressor_perch <- stepAIC(perchModel, direction = "both", trace = FALSE, k = 2)
```

```{r}
summary.lm(best_two_regressor_perch)
```


## Pike
```{r}
pikeFish = filter(fishALL, Species=='Pike') 
```

```{r}
pikeModel = lm(Weight~Length1+Length2+Length3+Height+Width, data= pikeFish)
```

```{r}
summary.lm(pikeModel)
```


### Best Models

```{r}
best_models_pike <- step(pikeModel)
summary.lm(best_models_pike)
```


### Best Two regressor model

```{r}
best_two_regressor_pike <- stepAIC(pikeModel, direction = "both", trace = FALSE, k = 2)
summary.lm(best_two_regressor_pike)
```


## Roach

```{r}
roachFish = filter(fishALL, Species=='Roach') 
roachModel = lm(Weight~Length1+Length2+Length3+Height+Width, data= roachFish)
summary.lm(roachModel)
```


### Best Models

```{r}
best_models_roach <- step(roachModel)
summary.lm(best_models_roach)
```


### Best Two regressor model

```{r}
best_two_regressor_roach <- stepAIC(roachModel, direction = "both", trace = FALSE, k = 2)
summary.lm(best_two_regressor_roach)
```


## Final Summary Statements

After analyzing the data, we found that for the Perch species, the best regressor model for predicting fish weight includes the predictors Length1, Length2, Length3, Height, and Width. Similarly, for the Pike and Roach species, the same set of predictors yielded the best regressor models. Additionally, to aid in model selection and stepwise regression, we had to add the MASS package to our R environment.